Computational Documents

### 2019-12-27 cd_compendium.Rmd
aha... let's move on... study is over

@@

>>>>

# 논문과 `ropensci` 진행경과 {#papers-ropensci}

[Ben Marwick, Carl Boettiger, Lincoln Mullen (2018), "Packaging Data Analytical Work Reproducibly
Using R (and Friends)", University of Wollongong
Research Online](https://ro.uow.edu.au/cgi/viewcontent.cgi?article=6445&context=smhpapers)

![재현가능한 과학연구를 위한 저작 방법](fig/compendium-rrtools.png)

- [`ropensci`, "Community Call: Reproducible Research with R"](https://ropensci.org/commcalls/2019-07-30/)

@@

- [시작이 반이다 - `start small`](cd-start-small.html)

```{r compendium-simple-paper, eval = FALSE}
project
|- DESCRIPTION
|- README.md  
|- Metadata.txt
|
|- data/                
|   +- 2014ParasiteSurveyJustBrood.csv
|   +- CedarBPLifeTable2014.csv
|   +- NorthBPLifeTable2013.txt
|   +- NorthBPLifeTable2014.csv|
|- analysis/
|   +- CodeforBPpaper.R
```

# 팩키지 개발 {#pkg-development}

- [팩키지 개발](cd-pkg-development.html)

```{r intermediate-decomposition, eval = FALSE}

project
|- DESCRIPTION
|- NAMESPACE
|- README.md
|- LakeTrophicModelling.Rproj
|
|- R/
|   +- LakeTrophicModelling-package.r
|   +- class_prob_rf.R
|   +- condAccuracy.R
|   +- crossval_rf.R
|   +- density_plot.R
|   +- ecdf_ks_ci.R
|   +- ecor_map.R
|   +- getCyanoAbund.R
|   +- getLakeIDs.R
|   +- importancePlot.R
|
|- man/
|   +- class_prob_rf.Rd
|   +- condAccuracy.Rd
|   +- crossval_rf.Rd
|   +- density_plot.Rd
|   +- ecdf_ks_ci.Rd
|   +- ecor_map.Rd
|   +- getCyanoAbund.Rd
|   +- getLakeIDs.Rd
|   +- importancePlot.Rd
|
|- data/                
|   +- LakeTrophicModelling.rda
|
|- vignettes/
|
|- inst/
|   +- doc/
|      +- manuscript.pdf
|   +- extdata/
|      +- ltmData.csv
|      +- data_def.csv

```

# CI/CD와 도커 {#cicd-docker}

`Dockerfile` 파일을 추가하여 환경도 재현가능하게 만들 수 있고, `.travis.yml`을 추가하여 CI/CD 환경도 구축할 수 있다. `tests/`를 추가하여 테스트 주도 개발(test-driven development, TDD)를 시도할 수 있고, 이를 통해 수작업 검증을 자동화하여 생산성과 품질을 대폭 향상시킬 수도 있다.

```{r cicd-docker, eval = FALSE}
project
|- DESCRIPTION          # project metadata and dependencies 
|- README.md            # top-level description of content and guide to users
|- NAMESPACE            # exports R functions in the package for repeated use
|- LICENSE              # specify the conditions of use and reuse of the code, data & text
|- .travis.yml          # continuous integration service hook for auto-testing at each commit
|- Dockerfile           # makes a custom isolated computational environment for the project
|
|- data/                # raw data, not changed once created
|  +- my_data.csv       # data files in open formats such as TXT, CSV, TSV, etc.
|
|- analysis/            # any programmatic code
|  +- my_report.Rmd     # R markdown file with narrative text interwoven with code chunks 
|  +- makefile          # builds a PDF/HTML/DOCX file from the Rmd, code, and data files
|  +- scripts/          # code files (R, shell, etc.) used for data cleaning, analysis and visualisation 
|
|- R/                     
|  +- my_functions.R    # custom R functions that are used more than once throughout the project
|
|- man/
|  +- my_functions.Rd   # documentation for the R functions (auto-generated when using devtools)
|
|- tests/
|  +- testthat.R        # unit tests of R functions to ensure they perform as expected
```

# 각 사례별 템플릿 {#case-by-case-template}

- [Jeff Hollister's manuscriptPackage](https://github.com/jhollist/manuscriptPackage)
- [Carl Boettiger's template](https://github.com/cboettig/template)
- [Francisco Rodriguez-Sanchez's template](https://github.com/Pakillo/template)
- [Ben Marwick's researchcompendium](https://github.com/benmarwick/researchcompendium)
    - [`rrtools`: Tools for Writing Reproducible Research in R](https://github.com/benmarwick/rrtools)

# `rrtoools` 워크샵 {#rrtools-workshop}

- ["Reproducible Research in R with rrtools", 31st October, Northwest Universities R Day](https://annakrystalli.me/rrtools-repro-research/index.html)
    - 공통: `devtools` 
    - 윈도우즈: [Rtools](https://cran.r-project.org/bin/windows/Rtools/)
    - 맥: [Xcode](https://developer.apple.com/xcode/)
    - 리눅스: `r-devel` 혹은 `r-base-dev`
